\boldmath Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-06-14 authors_responses/first_tac_rejection/authors_response.tex
Half way through response to reviewer 2

The proposed approach is interesting and the results are technically sound. The literature review is OK. But the organization of paper and its length make its reading difficult.}

\item \reviewtext{The reviewer encourages the authors to reorganize the article by greatly shortening it and to highlight the novelty.}

@@

@@

@@

>>>>

The proposed approach is interesting and the results are technically sound. The literature review is OK. But the organization of paper and its length make its reading difficult.

The reviewer encourages the authors to reorganize the article by greatly shortening it and to highlight the novelty.}

We're happy to hear that the results were found interesing and regret that the length and organisation has made the manuscript hard to read. We have heavily reorganised and rewritten parts of the work to make it easier to follow, including shortening the work by four pages. We hope that the flow of information is now easier to follow and that the method is more concisely described.

@@

We're sorry this was the case and agree with the reviewer that the introduction was too long. We have greatly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work. Our hope is that the new layout is easier to read and better suited to the target audience of the TAC journal.

@@

Thank you for pointing this out, this has now been added to the manuscript.

@@

Due to the number of components in the proposed method (encoding, encryption and estimation) our aim was to present the algorithm pseudocode as the summary of the method, but regret that this was not made clearer. We have rewritten and reorganised the localisation section and have tried to make a pseudocode summary, and its purpose, clearer. We hope that the updated manuscript better captures the overall summary of all presented components at the end of introduced components.
